---
title: "CRN Behavioral Experiment 2 - Report"
author: "Amir"
date: "11/24/2019"
output:
  html_document: default
  pdf_document: default
---

# Second Experiment

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, error = FALSE)
library(nFactors)
library(tidyverse)
library(reshape2)
library(lme4)
library(corrplot)
library(jtools)
library(dotwhisker)
library(broom)
library(knitr)
library(ggfortify)
library(nlme)
library(simr)
library(pscl)
library(foreign)
library("gdata")
library(psych)
library(GPArotation)
library('ri2')
#library(lmerTest)
library(grid)
library(eeptools)
library(ggthemes)
```

## Functions

```{r}
##### Plots setting
theme_Publication <- function(base_size=14, base_family="helvetica") {
     (theme_foundation()
       + theme(plot.title = element_text(face = "bold",
                                         size = rel(1.2), hjust = 0.5),
               text = element_text(),
               panel.background = element_rect(colour = NA),
               plot.background = element_rect(colour = NA),
               panel.border = element_rect(colour = NA),
               axis.title = element_text(face = "bold",size = rel(1)),
               axis.title.y = element_text(angle=90,vjust =2),
               axis.title.x = element_text(vjust = -0.2),
               axis.text = element_text(), 
               axis.line = element_line(colour="black"),
               axis.ticks = element_line(),
               panel.grid.major = element_line(colour="#f0f0f0"),
               panel.grid.minor = element_blank(),
               legend.key = element_rect(colour = NA),
               legend.position = "bottom",
               legend.direction = "horizontal",
               legend.key.size= unit(0.2, "cm"),
               legend.margin = unit(0, "cm"),
               legend.title = element_text(face="italic"),
               plot.margin=unit(c(10,5,5,5),"mm"),
               strip.background=element_rect(colour="#f0f0f0",fill="#f0f0f0"),
               strip.text = element_text(face="bold")
          ))
      
}

scale_fill_Publication <- function(...){
      library(scales)
      discrete_scale("fill","Publication",manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)
}

scale_colour_Publication <- function(...){
      library(scales)
      discrete_scale("colour","Publication",manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)
}
```

## Reading and cleaning the experiment data

```{r, echo=FALSE}
crn_experiment_data2 <- read_csv("/Users/atohidi/Dropbox (MIT)/Research/Projects/CRN-Project/Behavioral Experiment/Second Experiment/Data/Exp2_final_data.csv") %>% filter(Q1 == "I agree to participate", Finished == "True") %>% 
  slice(-(2:3)) 
```

```{r}
treatment <- crn_experiment_data2 %>% select(paste("image", 0:5, sep = "")) %>% 
  rowid_to_column("ID") %>% 
  gather(key = "image", value = "stimuli", ... = -ID) %>% arrange(ID) %>%
  separate(col = stimuli, into = c(NA, NA, NA, NA, "Publisher", "Article", "CRN", NA), sep = "_|/") %>% 
  separate(col = CRN, into = c("CRN", NA)) %>% select(-image)

trustworthy <- crn_experiment_data2 %>% select(Q722_1, Q729_1, Q730_1, Q731_1, Q732_1, Q733_1) %>% 
  rowid_to_column("ID") %>% 
  gather(key = "question", value = "trust", ... = -ID) %>% arrange(ID) %>% select(trust) %>%
  mutate(trust = unclass(factor(trust, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree nor disagree",
                                                 "Somewhat agree", "Strongly agree"))))

false <- crn_experiment_data2 %>% select(Q722_2, Q729_2, Q730_2, Q731_2, Q732_2, Q733_2) %>%  
  rowid_to_column("ID") %>% 
  gather(key = "question", value = "false", ... = -ID) %>% arrange(ID) %>% select(false) %>%
  mutate(false = unclass(factor(false, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree nor disagree",
                                                 "Somewhat agree", "Strongly agree"))))

biased <- crn_experiment_data2 %>% select(Q722_3, Q729_3, Q730_3, Q731_3, Q732_3, Q733_3) %>%  
  rowid_to_column("ID") %>% 
  gather(key = "question", value = "biased", ... = -ID) %>% arrange(ID) %>% select(biased) %>%
  mutate(biased = unclass(factor(biased, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree nor disagree",
                                                 "Somewhat agree", "Strongly agree"))))

credible <- crn_experiment_data2 %>% select(Q722_4, Q729_4, Q730_4, Q731_4, Q732_4, Q733_4) %>%  
  rowid_to_column("ID") %>% 
  gather(key = "question", value = "credible", ... = -ID) %>% arrange(ID) %>% select(credible) %>%
  mutate(credible = unclass(factor(credible, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree nor disagree",
                                                 "Somewhat agree", "Strongly agree"))))

informative <- crn_experiment_data2 %>% select(Q722_5, Q729_5, Q730_5, Q731_5, Q732_5, Q733_5) %>%  
  rowid_to_column("ID") %>% 
  gather(key = "question", value = "informative", ... = -ID) %>% arrange(ID) %>% select(informative) %>%
  mutate(informative = unclass(factor(informative, levels = c("Strongly disagree", "Somewhat disagree", "Neither agree nor disagree",
                                                 "Somewhat agree", "Strongly agree"))))

output2 <- cbind(treatment, trustworthy, false, biased, credible, informative) 
####### extracting some of the relevant features of the data from the survey

familiarity <- crn_experiment_data2 %>% select(Q845_12:Q845_19) %>% 
  rename(fox = Q845_12, atlantic = Q845_13, cnn = Q845_14, sacbee = Q845_15, 
         vox = Q845_16, daytonabeach = Q845_17, denverpost = Q845_18, usatoday = Q845_19) %>% 
  mutate_at(funs(factor), .vars = 1:8) %>% rowid_to_column("ID") %>% 
  inner_join(treatment, by = "ID") %>% select(-Article, -CRN) %>% 
  gather(key = "Source", value = "familiarity", ... = -c(Publisher,ID)) %>%
  filter(Publisher == Source) %>% arrange(ID) %>% select(ID, Publisher, familiarity) 

# imputing NAs in familiarity with No
familiarity$familiarity <- ifelse(is.na(familiarity$familiarity) , "No", familiarity$familiarity)
output2 <- inner_join(output2, familiarity)

# media_balance <- crn_experiment_data2 %>% select(Q384_12:Q384_19) %>% 
#   rename(fox = Q384_12, atlantic = Q384_13, cnn = Q384_14, sacbee = Q384_15, 
#          vox = Q384_16, daytonabeach = Q384_17, denverpost = Q384_18, usatoday = Q384_19) %>% 
#   mutate_at(funs(factor), .vars = 1:8) %>% rowid_to_column("ID") %>% 
#   inner_join(treatment, by = "ID") %>% select(-Article, -CRN) %>% 
#   gather(key = "Source", value = "media_balance", ... = -c(Publisher,ID)) %>%
#   filter(Publisher == Source) %>% arrange(ID) %>% select(ID, Publisher, media_balance)

features <- crn_experiment_data2 %>% select(Q735, Q737, Q32, Q42, Q3, Q2, Q14, Q738, Q740) %>%
  rename(ad_notice = Q735, ad_blocker = Q737, pol_leaning = Q32, nct_1 = Q738, nct_2 = Q740, 
         pol_interest=Q42, age=Q3, gender=Q2, education=Q14) %>% rowid_to_column("ID") %>% 
  mutate(nct_1 = as.numeric(nct_1 == "Like it"), nct_2 = as.numeric(nct_2 == "Complex")) %>% 
  mutate(age = 2019 - as.numeric(age)) %>% 
  mutate(nfc_score = nct_1 + nct_2) %>%
  mutate_at(funs(factor), .vars = c("ad_notice", "ad_blocker", "pol_leaning", "pol_interest", "gender", "education"))

screeners <- crn_experiment_data2 %>% rowid_to_column(var = "ID") %>% 
  select(ID, Q773, Q797, Q1_1, Q1_6) %>% 
  rename(scr_color = Q773, scr_web = Q797, scr_grid_ww2 = Q1_1, scr_grid_middle = Q1_6) %>%
  mutate(scr_color = as.numeric(scr_color == "Red,Green"), 
         scr_web = as.numeric(scr_web == "The Drudge Report,ABC News website"), 
         scr_grid_ww2 = as.numeric(scr_grid_ww2 == "Disagree\nstrongly" | scr_grid_ww2 == "Disagree"),
         scr_grid_middle = as.numeric(scr_grid_middle == "Neither agree nor disagree")) %>% 
  mutate(attention = scr_color + scr_web + scr_grid_ww2 + scr_grid_middle)

output2 <- inner_join(output2, inner_join(features, screeners))

# pol_interest <- crn_experiment_data2 %>% dplyr::select(Q42) %>% rename (pol_interest=Q42) %>% rowid_to_column("ID")
# pol_interest$pol_interest[pol_interest$pol_interest == "Hardly at all"] <- 1
# pol_interest$pol_interest[pol_interest$pol_interest == "Only now and then"] <- 2
# pol_interest$pol_interest[pol_interest$pol_interest == "Some of the time"] <- 3
# pol_interest$pol_interest[pol_interest$pol_interest == "Most of the time"] <- 4
# output2 <- inner_join(output2, inner_join(pol_interest, features))

# age <- crn_experiment_data2 %>% dplyr::select(Q3) %>% rename (age=Q3) %>% rowid_to_column("ID")
# age$age <- as.Date(age$age, format = "%Y")
# age$age[is.na(age$age)] <- Sys.Date()
# age$age <- floor(age_calc(age$age, units = "years"))
# age$bin_age <- cut(age$age, seq(0, 90, 10))
# output2 <- inner_join(output2, inner_join(age, features))

# gender <- crn_experiment_data2 %>% dplyr::select(Q2) %>% rename(gender=Q2) %>% rowid_to_column("ID")
# output2 <- inner_join(output2, inner_join(as.factor(gender), features))

# education <- crn_experiment_data2 %>% dplyr::select(Q14) %>% rename (education=Q14) %>% rowid_to_column("ID")
# education$education_level <- education$education
# education$education_level[education$education_level == "Did not graduate from high school"] <- 1
# education$education_level[education$education_level == "High school graduate"] <- 2
# education$education_level[education$education_level == "Some college, but no degree"] <- 3
# education$education_level[education$education_level == "2-year college degree"] <- 4
# education$education_level[education$education_level == "4-year college degree"] <- 5
# education$education_level[education$education_level == "Postgraduate degree (MA, MBA, JD, PhD, etc.)"] <- 6
# output2 <- inner_join(output2, inner_join(education, features))

# nct <- crn_experiment_data2 %>% rowid_to_column(var = "ID") %>% 
#   dplyr::select(ID, Q738, Q740) %>% 
#   rename(nct_1 = Q738, nct_2 = Q740) %>%
#   mutate(nct_1 = as.numeric(nct_1 == "Like it"), 
#          nct_2 = as.numeric(nct_2 == "Complex")) %>% 
#   mutate(nfc_score = nct_1 + nct_2)
# output2 <- inner_join(output2, inner_join(features, nct))

#creating separate columns for different treatment conditions

output2 <- output2 %>% mutate(fam_rate = ifelse(Publisher %in% c("cnn", "fox", "usatoday"), "High", 
                                ifelse(Publisher %in% c("atlantic", "denverpost", "vox"), "Medium", "Low"))) %>%
  mutate(pol_rate = ifelse(Publisher %in% c("cnn", "atlantic", "vox"), "Liberal", ifelse(Publisher %in% c("fox"), "Conservative", "Neutral/Local"))) %>%
  mutate(Batch = ifelse(Publisher %in% c("cnn", "fox", "denver_post", "vox"), 1, 2)) %>%
  mutate(CRN_leaning = ifelse(CRN == "hqpol" &  Batch == 1, "Left", 
                              ifelse(CRN == "hqpol" & Batch == 2, "Right", "Neutral"))) %>%
  mutate_at(.funs = factor, .vars = "CRN_leaning") %>%
  mutate(CRN_quality_general = ifelse(CRN %in% c("lq", "lqpol"), "Lq", 
                              ifelse(CRN %in% c("hq", "hqpol"), "Hq", "NA"))) %>%
  mutate(CRN_quality_Pol = if_else(CRN %in% c("hqpol"), "Hq",
                if_else(CRN %in% c("lqpol"), "Lq",
                if_else(CRN %in% c("na"), "nap", if_else(CRN %in% c("hq", "lq"), "nose", "NA") ))))  %>%
  mutate(CRN_quality_NonPol = ifelse(CRN %in% c("lq"), "Lq", 
                              ifelse(CRN %in% c("hq"), "Hq", 
                              if_else(CRN %in% c("na"), "nap", if_else(CRN %in% c("hqpol", "lqpol"), "nose", "NA"))))) %>%
  mutate(CRN_type = ifelse(CRN %in% c("lqpol", "hqpol"), "Pol", 
                              ifelse(CRN %in% c("lq", "hq"), "NonPol", "NA"))) %>%
  mutate_at(.funs = factor, .vars = c("CRN_type", "CRN_quality_general", "CRN_quality_Pol", "CRN_quality_NonPol", "fam_rate", "pol_rate", "Publisher", "Article", "CRN",  "familiarity", "ad_notice", "ad_blocker", "pol_leaning")) %>%
  mutate(CRN_vs_NA = 1/3*as.numeric(CRN_quality_general == "Lq") + 1/3*as.numeric(CRN_quality_general == "Hq") -
           2/3 * as.numeric(CRN_quality_general == "NA"),
         Hq_vs_Lq = 1/2*as.numeric(CRN_quality_general == "Hq") - 1/2*as.numeric(CRN_quality_general == "Lq"),
           Hq_vs_NA = 1/2*as.numeric(CRN_quality_general == "Hq") - 1/2*as.numeric(CRN_quality_general == "NA"),
  Clickbait_vs_NA = 1/2*as.numeric(CRN_quality_general == "Lq") - 1/2*as.numeric(CRN_quality_general == "NA")) %>%
  mutate(CRN_vs_NA_pol = 1/3*as.numeric(CRN_quality_Pol == "Lq") + 1/3*as.numeric(CRN_quality_Pol == "Hq") -
           2/3 * as.numeric(CRN_quality_Pol == "nap"),
         Hq_vs_Lq_pol = 1/2*as.numeric(CRN_quality_Pol == "Hq") - 1/2*as.numeric(CRN_quality_Pol == "Lq")) %>%
  mutate(CRN_vs_NA_nonpol = 1/3*as.numeric(CRN_quality_NonPol == "Lq") + 1/3*as.numeric(CRN_quality_NonPol == "Hq") -
           2/3 * as.numeric(CRN_quality_NonPol == "nap"),
         Hq_vs_Lq_nonpol = 1/2*as.numeric(CRN_quality_NonPol == "Hq") - 1/2*as.numeric(CRN_quality_NonPol == "Lq")) %>%
mutate(Political_vs_NonPolitical = 1/2*as.numeric(CRN_type == "Pol") - 1/2*as.numeric(CRN_type == "NonPol"))

output2$CRN_quality_general <- factor(output2$CRN_quality_general, levels(output2$CRN_quality_general)[c(3,2,1)])
output2$CRN_quality_Pol <- factor(output2$CRN_quality_Pol, levels(output2$CRN_quality_Pol)[c(3,2,1)])
output2$CRN_quality_NonPol <- factor(output2$CRN_quality_NonPol, levels(output2$CRN_quality_NonPol)[c(3,2,1)])
output2$CRN_type <- factor(output2$CRN_type, levels(output2$CRN_type)[c(3,2,1)])
output2$CRN_leaning <- factor(output2$CRN_leaning, levels(output2$CRN_leaning)[c(3,1,2)])


#imputing missing responses with the mean score for that user

output2$false_inverse <- 6 - output2$false
output2$biased_inverse <- 6 - output2$biased
output2$mean_estimate <- rowMeans(subset(output2, 
                                         select = c(trust, informative, credible, false_inverse, biased_inverse)), na.rm = TRUE)

output2$mean_estimate_positive <- rowMeans(subset(output2, select = c(trust, informative, credible)), na.rm = TRUE)

output2$mean_estimate_negative <- rowMeans(subset(output2, select = c(false_inverse, biased_inverse)), na.rm = TRUE)
output2[, "max_estimate"] <- apply(output2[,c("trust", "informative", "credible", "false_inverse", "biased_inverse")], 1, max, na.rm = TRUE)

output2$trust <- ifelse(is.na(output2$trust), output2$mean_estimate, output2$trust)
output2$credible <- ifelse(is.na(output2$credible), output2$mean_estimate, output2$credible)
output2$informative <- ifelse(is.na(output2$informative), output2$mean_estimate, output2$informative)
output2$false_inverse <- ifelse(is.na(output2$false_inverse), output2$mean_estimate, output2$false_inverse)
output2$biased_inverse <- ifelse(is.na(output2$biased_inverse), output2$mean_estimate, output2$biased_inverse)
output2$false <- 6 - output2$false_inverse
output2$biased <- 6 - output2$biased_inverse

## Remove the people who have NaNs mean estimate (who replied to 0 questions for one article), there are 13 such persons 
output2 <- output2 %>% filter(is.na(output2$mean_estimate) == 0)

######### computing principal components
output_pca <- prcomp(dplyr::select(output2, trust:informative), 
                     center = TRUE, scale. = TRUE)
#summary(output_pca)
autoplot(output_pca, data = output2, colour = "CRN", loadings = TRUE,
         loadings.label = TRUE)
output2 <- output2 %>% mutate(PC1 = output_pca$x[,1], PC2 = output_pca$x[,2])

pca_sigma <- as.data.frame(t(apply(output2 %>% filter(CRN == "na") %>%
              dplyr::select(PC1, PC2), 2, sd)))

#output2 <- output2 %>% mutate(avg =1/5*(trust+(5-false_inverse)+(5-biased_inverse)+credible+informative))

avg_sigma <- sd((output2 %>% filter(CRN == "na"))$mean_estimate)

```

## Some interesting plots

#### Plotting Dot product and Rank Correlation for credibility measures

```{r, echo=FALSE}
correlation <- cor(select(output2, trust:informative))
rank_correlation <- cor(dplyr::select(output2, trust:informative), 
                        method = "spearman")
corrplot(correlation, type="upper", method = "number", 
         title = "dot product correlation")
corrplot(rank_correlation, type="upper", method = "number")
```

#### Histogram of political leaning

```{r}
output2 %>% group_by(ID) %>% 
  summarise(pol_leaning = unique(pol_leaning)) %>% filter(pol_leaning != "") %>%
  ggplot(aes(x = pol_leaning)) + geom_bar() + 
  ggtitle("Histogram of political leaning") %>% theme_Publication() 
```


#### Mean response to different questions for each publisher

```{r, echo=FALSE}
output2 %>% gather ("question", "answer", trust:informative) %>% 
  group_by(Publisher, question) %>% 
  summarise(mean_response = mean(answer)) %>% ungroup() %>% 
  ggplot(aes(x = Publisher, y = mean_response)) +
  geom_col(position = "dodge2") + facet_wrap(~ question) + theme_Publication() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle("Mean response to different questions") 
```

```{r, echo=FALSE}
output2 %>% gather ("question", "answer", trust:informative) %>% 
  group_by(Publisher, question, familiarity) %>% 
  summarise(mean_response = mean(answer)) %>% ungroup() %>% 
  ggplot(aes(x = Publisher, y = mean_response, fill = familiarity)) +
  geom_col(position = "dodge2") + facet_wrap(~ question) + theme_Publication() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle("Mean response to different questions and user familiarity condition")
```
#### Mean response based on party affiliation

```{r}
output2 %>% select(mean_estimate, pol_leaning, Publisher) %>% na.omit() %>%
  gather ("question", "answer", mean_estimate) %>% 
  group_by(Publisher, question, pol_leaning) %>% 
  summarise(mean_response = mean(answer)) %>% ungroup() %>% 
  ggplot(aes(x = Publisher, y = mean_response, fill = pol_leaning)) +
  geom_col(position = "dodge2") + facet_wrap(~ question) +
  ggtitle("Mean response based on average score, for different publishers and party affiliations") + 
  theme_Publication() + scale_colour_Publication() + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  xlab("")

```


#### Histogram of CRN conditions 

```{r}
output2 %>% ggplot(aes(x = CRN, fill = familiarity)) + 
  geom_bar() + 
  facet_wrap(~ Publisher, nrow = 1) + 
  ggtitle("Histogram of CRN conditions") + theme_Publication() + scale_colour_Publication()  + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
```

#### Screener questions

```{r}
output2 %>%
  ggplot(aes(x = attention)) + 
  geom_bar(aes(y = (..count..)/sum(..count..))) +
  ggtitle("Histogram of correct responses to screener questions") + theme_Publication() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ylab("perc")
```


#### Familiarity with different Publishers

```{r}
familiarity %>% na.omit() %>% group_by(Publisher) %>%
  summarise(prop = sum(familiarity == "Yes")/n()) %>% 
  arrange(desc(prop)) %>%
  ggplot() + geom_col(mapping = aes(x = reorder(Publisher, -prop), y = prop)) + 
  scale_y_continuous(labels = scales::percent_format()) + ylab("") + 
  xlab("") + ggtitle("Familiarity rate of Publishers") + theme_Publication() + scale_colour_Publication() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  geom_hline(yintercept=.5, linetype="dashed", color = "red") + geom_hline(yintercept=.25, linetype="dashed", color = "red")
```
### Familiarity rates based on party affiliations

```{r}
 output2 %>% select(familiarity, pol_leaning) %>% na.omit() %>%
  ggplot(aes(x = pol_leaning, fill = familiarity)) + 
   geom_bar(position = "dodge2") + 
   theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
   xlab("") + ggtitle("Familiarity with the publisher based on party affiliations") + 
   ylab("prop")
```

### Fraction of people who noticed CRNs based on ad blocker used

```{r}
output2 %>% select(ad_notice, ad_blocker) %>% na.omit() %>% 
  ggplot(aes(x = ad_notice, fill = ad_blocker)) + 
  geom_bar(aes(y = (..count..)/sum(..count..))) + theme_Publication() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  xlab("") + ggtitle("Fraction of people who noticed CRNs") + 
  ylab("fraction")
```

### Relation of noticing ads and attention

```{r eval = FALSE}
output2 %>% select(ad_notice, attention) %>% na.omit() %>% mutate_at(funs(factor), .vars = "attention") %>%
  ggplot(aes(x = ad_notice, fill = attention)) + 
  geom_bar(aes(y = (..count..)/sum(..count..))) + theme_Publication() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  xlab("") + ggtitle("Fraction of people who noticed CRNs") + 
  ylab("")

output2 %>% select(ad_notice, attention) %>% na.omit() %>% mutate_at(funs(factor), .vars = "attention") %>% 
  select(ad_notice, attention) %>%
  group_by(ad_notice) %>% mutate(total = n()) %>% ungroup() %>%
  group_by(attention, ad_notice) %>% mutate(count = n()) %>% unique() %>%
  summarise(perc = count/total) %>% 
  ggplot(aes(x = ad_notice, y = perc, fill = attention)) + 
  geom_bar(stat="identity") + theme_Publication()
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  xlab("") + ggtitle("Fraction of people who noticed CRNs") + ylab("")
```


## Hypothesis 1: 

#### Analysis based on principal components

```{r}
# distinguishing the effect of ads in general and high quality ads vs low quality ones
lmer(data = output2,
     formula = PC1/pca_sigma$PC1 ~ (1|ID) + (1|Publisher) + (1|Article) +
                                   familiarity  + pol_leaning + pol_interest + fam_rate + 
                                   ad_notice + age + gender + education + attention + nfc_score + 
                                   CRN_vs_NA:fam_rate + Hq_vs_Lq:fam_rate) %>% 
  tidy() %>% filter(str_detect(term, "CRN") | str_detect(term, "Hq")) %>%
  dwplot(dodge_size = 0.6) + xlab("ATE for the first principal component") +     
  geom_vline(xintercept = 0, color = "black", alpha = 0.5, linetype = "longdash") + theme_Publication() + scale_colour_Publication()

# seperating the effect of ads based on their quality (comparing Hq and Lq with NA)
lmer(data = output2,
     formula = PC1/pca_sigma$PC1 ~ (1|ID) + (1|Publisher) + (1|Article) +
                                   familiarity  + pol_leaning + pol_interest + fam_rate + 
                                   ad_notice + age + gender + education + attention + nfc_score + 
                                   CRN_quality_general:fam_rate) %>% 
  tidy() %>% filter(str_detect(term, "CRN")) %>%
  dwplot(dodge_size = 0.6) + xlab("ATE for the first principal component") +     
  geom_vline(xintercept = 0, color = "black", alpha = 0.5, linetype = "longdash") + theme_Publication() + scale_colour_Publication()


lmer(data = output2,
     formula = PC2/pca_sigma$PC2 ~ (1|ID) + (1|Publisher) + (1|Article) +
                                   familiarity  + pol_leaning + pol_interest + fam_rate + 
                                   ad_notice + age + gender + education + attention + nfc_score + 
                                   CRN_vs_NA:fam_rate + Hq_vs_Lq:fam_rate) %>% 
  tidy() %>% filter(str_detect(term, "CRN") | str_detect(term, "Hq")) %>%
  dwplot(dodge_size = 0.6) + xlab("ATE for the second principal component") +     
  geom_vline(xintercept = 0, color = "black", alpha = 0.5, linetype = "longdash") + theme_Publication() + scale_colour_Publication()


lmer(data = output2,
     formula = PC2/pca_sigma$PC2 ~ (1|ID) + (1|Publisher) + (1|Article) +
                                   familiarity  + pol_leaning + pol_interest + fam_rate + 
                                   ad_notice + age + gender + education + attention + nfc_score + 
                                   CRN_quality_general:fam_rate) %>% 
  tidy() %>% filter(str_detect(term, "CRN")) %>%
  dwplot(dodge_size = 0.6) + xlab("ATE for the second principal component") +     
  geom_vline(xintercept = 0, color = "black", alpha = 0.5, linetype = "longdash") + theme_Publication() + scale_colour_Publication()

```

### Analysis based on the average score

#### Main effect, without including the heterogeneity

```{r}
# distinguishing the effect of ads in general and high quality ads vs low quality ones
lmer(data = output2,
     formula = mean_estimate/avg_sigma ~ (1|ID) + (1|Publisher) + (1|Article) +
                                   familiarity  + pol_leaning + pol_interest + fam_rate + 
                                   ad_notice + age + gender + education + attention + nfc_score + 
                                   CRN_vs_NA + Hq_vs_Lq) %>% 
  tidy() %>% filter(str_detect(term, "CRN") | str_detect(term, "Hq")) %>%
  dwplot(dodge_size = 0.6) + xlab("ATE for the average score") +     
  geom_vline(xintercept = 0, color = "black", alpha = 0.5, linetype = "longdash") + theme_Publication() + scale_colour_Publication()

# seperating the effect of ads based on their quality (comparing Hq and Lq with NA)
lmer(data = output2,
     formula = mean_estimate/avg_sigma  ~ (1|ID) + (1|Publisher) + (1|Article) +
                                   familiarity  + pol_leaning + pol_interest + fam_rate + 
                                   ad_notice + age + gender + education + attention + nfc_score + 
                                   CRN_quality_general) %>% 
  tidy() %>% filter(str_detect(term, "CRN")) %>%
  dwplot(dodge_size = 0.6) + xlab("ATE for the average score") +     
  geom_vline(xintercept = 0, color = "black", alpha = 0.5, linetype = "longdash") + theme_Publication() + scale_colour_Publication()

# seperating effect of political ads non-political ones
lmer(data = output2,
     formula = mean_estimate/avg_sigma  ~ (1|ID) + (1|Publisher) + (1|Article) +
                                   familiarity  + pol_leaning + pol_interest + fam_rate + 
                                   ad_notice + age + gender + education + attention + nfc_score + 
                                   CRN_type) %>% 
  tidy() %>% filter(str_detect(term, "CRN")) %>%
  dwplot(dodge_size = 0.6) + xlab("ATE for the average score") +     
  geom_vline(xintercept = 0, color = "black", alpha = 0.5, linetype = "longdash") + theme_Publication() + scale_colour_Publication()
```

#### Investigating the heterogeneity among different familiarity rates of publishers

```{r}
# distinguishing the effect of ads in general and high quality ads vs low quality ones
lmer(data = output2,
     formula = mean_estimate/avg_sigma ~ (1|ID) + (1|Publisher) + (1|Article) +
                                   familiarity  + pol_leaning + pol_interest + fam_rate + 
                                   ad_notice + age + gender + education + attention + nfc_score + 
                                   CRN_vs_NA:fam_rate + Hq_vs_Lq:fam_rate) %>% 
  tidy() %>% filter(str_detect(term, "CRN") | str_detect(term, "Hq")) %>%
  dwplot(dodge_size = 0.6) + xlab("ATE for the average score") +     
  geom_vline(xintercept = 0, color = "black", alpha = 0.5, linetype = "longdash") + theme_Publication() + scale_colour_Publication()

# seperating the effect of ads based on their quality (comparing Hq and Lq with NA)
lmer(data = output2,
     formula = mean_estimate/avg_sigma  ~ (1|ID) + (1|Publisher) + (1|Article) +
                                   familiarity  + pol_leaning + pol_interest + fam_rate + 
                                   ad_notice + age + gender + education + attention + nfc_score + 
                                   CRN_quality_general:fam_rate) %>% 
  tidy() %>% filter(str_detect(term, "CRN")) %>%
  dwplot(dodge_size = 0.6) + xlab("ATE for the average score") +     
  geom_vline(xintercept = 0, color = "black", alpha = 0.5, linetype = "longdash") + theme_Publication() + scale_colour_Publication()

# seperating effect of political ads non-political ones
lmer(data = output2,
     formula = mean_estimate/avg_sigma  ~ (1|ID) + (1|Publisher) + (1|Article) +
                                   familiarity  + pol_leaning + pol_interest + fam_rate + 
                                   ad_notice + age + gender + education + attention + nfc_score + 
                                   CRN_type:fam_rate) %>% 
  tidy() %>% filter(str_detect(term, "CRN")) %>%
  dwplot(dodge_size = 0.6) + xlab("ATE for the average score") +     
  geom_vline(xintercept = 0, color = "black", alpha = 0.5, linetype = "longdash") + theme_Publication() + scale_colour_Publication()

```

#### including the heterogeneity of user specific familiarity with the publisher 

```{r}
lmer(data = output2,
     formula = mean_estimate/avg_sigma ~ (1|ID) + (1|Publisher) + (1|Article) +
                                   familiarity  + pol_leaning + pol_interest + fam_rate + 
                                   ad_notice + age + gender + education + attention + nfc_score + fam_rate:familiarity + 
                                   CRN_vs_NA:fam_rate:familiarity + Hq_vs_Lq:fam_rate:familiarity) %>% 
  tidy() %>% filter(str_detect(term, "CRN") | str_detect(term, "Hq")) %>%
  dwplot(dodge_size = 0.6) + xlab("ATE for the average score") +     
  geom_vline(xintercept = 0, color = "black", alpha = 0.5, linetype = "longdash") + theme_Publication() + scale_colour_Publication()

# seperating the effect of ads based on their quality (comparing Hq and Lq with NA)
lmer(data = output2,
     formula = mean_estimate/avg_sigma  ~ (1|ID) + (1|Publisher) + (1|Article) +
                                   familiarity  + pol_leaning + pol_interest + fam_rate + 
                                   ad_notice + age + gender + education + attention + nfc_score + fam_rate:familiarity + 
                                   CRN_quality_general:fam_rate:familiarity) %>% 
  tidy() %>% filter(str_detect(term, "CRN")) %>%
  dwplot(dodge_size = 0.6) + xlab("ATE for the average score") +     
  geom_vline(xintercept = 0, color = "black", alpha = 0.5, linetype = "longdash") + theme_Publication() + scale_colour_Publication()

```

### The effect of ad recognition on publisher evaluation

```{r}
lmer(data = output2,
     formula = mean_estimate/avg_sigma ~ (1|ID) + (1|Publisher) + (1|Article) +
                                   familiarity  + pol_leaning + pol_interest + fam_rate + 
                                   ad_notice + age + gender + education + attention + nfc_score + fam_rate:ad_notice + 
                                   CRN_quality_general:fam_rate:ad_notice) %>% 
  tidy() %>% 
  filter(str_detect(term, "CRN") & str_detect(term, "Medium")) %>%
  dwplot(dodge_size = 0.6) + xlab("Mean outcome ATE") +     
  geom_vline(xintercept = 0, color = "black", alpha = 0.5, linetype = "longdash") + theme_Publication() + scale_colour_Publication()


lmer(data = output2,
     formula = mean_estimate/avg_sigma ~ (1|ID) + (1|Publisher) + (1|Article) +
                                                familiarity + pol_leaning + 
                                                CRN_vs_NA:fam_rate:ad_notice + Hq_vs_Lq:fam_rate:ad_notice) %>% 
  tidy() %>% 
  filter(str_detect(term, "CRN")  ) %>%
  dwplot(dodge_size = 0.6) + xlab("Mean outcome ATE") +     
  geom_vline(xintercept = 0, color = "black", alpha = 0.5, linetype = "longdash") + 
  scale_colour_Publication() + theme_Publication()
```


## Hypothesis 2: 
###  Is it not in the publishers’ interest to embed ads with a leaning that differ from theirs?

```{r}
lmer(output2, formula = mean_estimate/avg_sigma ~ (1|ID) + (1|Publisher) + (1|Article) +
                                   familiarity  + pol_leaning + pol_interest + fam_rate + pol_rate +
                                   ad_notice + age + gender + education + attention + nfc_score + 
                                            pol_rate:CRN_leaning) %>% 
  tidy() %>% filter(str_detect(term, "CRN")) %>% 
  dwplot(dodge_size = 0.6) + xlab("ATE for the average score") +     
  geom_vline(xintercept = 0, color = "black", alpha = 0.5, linetype = "longdash") + theme_Publication() + scale_colour_Publication()
```



## Factor Analysis

### Parallel Analysis

```{r}
X <- dplyr::select(output2, trust:informative)
ev <- eigen(cor(X)) # get eigenvalues
ap <- parallel(subject=nrow(X),var=ncol(X), rep=100, cent=.05)
nS <- nScree(x=ev$values, aparallel=ap$eigen$qevpea)
plotnScree(nS)
```

### Exploratory Factor Analysis

```{r}
two_factor <- fa(r = cor(X), nfactors = 2, rotate = "varimax", fm = "minres")
print(two_factor)
print(two_factor$loadings,cutoff = 0.3)
fa.diagram(two_factor)
```

## Normalizing effects in terms of heterogeneity of effect sizes among different pulishers or political leanings

```{r}
# max difference in mean responses to publishers: Max -> CNN, Min -> Daytonabeach
mean_per_publisher <- output2 %>% group_by(Publisher) %>% summarise(mean_per_publisher = mean(mean_estimate)) %>%
  arrange(-mean_per_publisher) %>% select(mean_per_publisher)
max_diff_in_mean <- max(mean_per_publisher$mean_per_publisher) - min(mean_per_publisher$mean_per_publisher)

# max difference in mean responses to publishers only for NA condition: Max -> Vox, Min -> Daytonabeach
mean_per_publisher_na <- output2 %>% filter(CRN == "na") %>% group_by(Publisher) %>% 
  summarise(mean_per_publisher = mean(mean_estimate)) %>%
  arrange(-mean_per_publisher) %>% select(mean_per_publisher)
max_diff_in_mean_na <- max(mean_per_publisher_na$mean_per_publisher) - min(mean_per_publisher_na$mean_per_publisher)

# difference in mean ratings between Democrats and Republicans
pol_mean <- output2 %>% group_by(pol_leaning) %>% summarise(pol_mean = mean(mean_estimate)) %>% 
  filter(pol_leaning %in% c("Democrat","Republican"))
diff_in_mean_pol <- max(pol_mean$pol_mean) - min(pol_mean$pol_mean)

# partisan difference, democrats rating for CNN - republican's rating for fox
democrat_CNN <- output2 %>% filter(pol_leaning == "Democrat" & Publisher == "vox", CRN == "na") %>% summarise(CNN_dem = mean(mean_estimate))
republican_FOX <- output2 %>% filter(pol_leaning == "Republican" & Publisher == "vox", CRN == "na") %>% summarise(Fox_rep = mean(mean_estimate))
partisan_dif <- democrat_CNN$CNN_dem - republican_FOX$Fox_rep

#normalizing_factor <- max_diff_in_mean_na 
normalizing_factor <- diff_in_mean_pol

# distinguishing the effect of ads in general and high quality ads vs low quality ones
lmer(data = output2,
     formula = mean_estimate/normalizing_factor ~ (1|ID) + (1|Publisher) + (1|Article) +
                                   familiarity  + pol_leaning + pol_interest + fam_rate + 
                                   ad_notice + age + gender + education + attention + nfc_score + 
                                   CRN_vs_NA:fam_rate + Hq_vs_Lq:fam_rate) %>% 
  tidy() %>% filter(str_detect(term, "CRN") | str_detect(term, "Hq")) %>%
  dwplot(dodge_size = 0.6) + xlab("ATE for the average score") +     
  geom_vline(xintercept = 0, color = "black", alpha = 0.5, linetype = "longdash") + theme_Publication() + scale_colour_Publication()

# seperating the effect of ads based on their quality (comparing Hq and Lq with NA)
lmer(data = output2,
     formula = mean_estimate/normalizing_factor  ~ (1|ID) + (1|Publisher) + (1|Article) +
                                   familiarity  + pol_leaning + pol_interest + fam_rate + 
                                   ad_notice + age + gender + education + attention + nfc_score + 
                                   CRN_quality_general:fam_rate) %>% 
  tidy() %>% filter(str_detect(term, "CRN")) %>%
  dwplot(dodge_size = 0.6) + xlab("ATE for the average score") +     
  geom_vline(xintercept = 0, color = "black", alpha = 0.5, linetype = "longdash") + theme_Publication() + scale_colour_Publication()

# seperating effect of political ads non-political ones
lmer(data = output2,
     formula = mean_estimate/normalizing_factor  ~ (1|ID) + (1|Publisher) + (1|Article) +
                                   familiarity  + pol_leaning + pol_interest + fam_rate + 
                                   ad_notice + age + gender + education + attention + nfc_score + 
                                   CRN_type:fam_rate) %>% 
  tidy() %>% filter(str_detect(term, "CRN")) %>%
  dwplot(dodge_size = 0.6) + xlab("ATE for the average score") +     
  geom_vline(xintercept = 0, color = "black", alpha = 0.5, linetype = "longdash") + theme_Publication() + scale_colour_Publication()
```




